Cover Letter

### 2017-12-10 paper/sections/6_results.tex
paper: experimental setup, popper (#27, #30)
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

%We run experiments on the same cluster and normalize results to control for
%hardware differences and to make our results more generally applicable and
%reproducible\footnote{ This paper adheres to The Popper
%Convention~\cite{jimenez_popper_2016}, so experiments presented here are
%available in the repository for this article.  Experiments can be examined in
%more detail, or even re-run, by visiting the \texttt{[source]} link next to
%each figure. That link points to a Jupyter notebook that shows the analysis and
%source code for that graph, which points to an experiment and its artifacts.}.
%We use a CloudLab cluster of 34 nodes, each with 16 2.4 GHz CPUs, 128GB RAM,
%and SSDs.  Each node uses Ubuntu 14.04 and We develop on Ceph's Jewel release,
%version 10.2.1, which was released in May 2016. All daemons run as a single
%process (the default setting for Ceph) and the Ceph
%components\footnote{http://docs.ceph.com/docs/jewel/rados/} are: 1 monitor, 3
%object storage daemons, 1 metadata server, and 29 clients.

>>>>

\newcomment{We run experiments on the same cluster and normalize results to
control for hardware differences and to make our results more generally
applicable. We use a CloudLab cluster of 34 nodes connected with 10Gbit
ethernet, each with 16 2.4 GHz CPUs, 128GB RAM, and SSDs.  Each node uses
Ubuntu 14.04 and we develop on Ceph's Jewel release, version 10.2.1, which was
released in May 2016. All daemons run as a single process (the default setting
for Ceph) and the Ceph
components\footnote{http://docs.ceph.com/docs/jewel/rados/} are: 1 monitor, 3
object storage daemons, 1 metadata server, and 29 clients.}

\newcomment{We understand concerns about cluster size and network, especially
for systems aimed at HPC but our evaluation focuses on verifying the behavior of
different techniques in the same global namespace. These techniques have
already proven to be effective and scalable in systems that specialize an
entire namespace according to a single optimization strategy (e.g., Lustre,
BatchFS, DeltaFS), so our evaluation explores the behavior of the
consistency/durability mechanisms and their effect with/without isolation.}

\newcomment{To make our results reproducible, this paper adheres to The Popper
Convention~\cite{jimenez_popper_2016}, so experiments presented here are
available in the repository for this article.  Experiments can be examined in
more detail, or even re-run, by visiting the \texttt{[source]} link next to
each figure. That link points to a Jupyter notebook that shows the analysis and
source code for that graph, which points to an experiment and its artifacts.}
\addressesissue{1}
